**Measuring Depression and Anxiety with 4 items? Adaptation of the PHQ-4 to increase its Sensitivity to Subclinical Variability**

### 2024-12-11 paper/4_WIP/manuscript.qmd
Update manuscript.qmd
@AnafNeves

**TODO** (describe BDI-II, STAI-5, PHQ-4, and other measures used but not relevant)

The total scores for the original version are 0-6 scores for depression and anxiety. The refined version creates more possible scores (0.5, 1.5, 2.5, etc.) due to the presence of an item scored 0.5.

@@

**TODO**

>>>>

Participants were randomly assigned to complete either the original or refined version of the PHQ-4, which included one additional response option ("Once or twice") scored 0.5 (creating more possible total scores - 0.5, 1.5, 2.5, etc.).

The BDI-II [@beck1996beck] was used as a ground truth measure of depressive symptoms. It includes 21 items, each addressing a specific depression symptom and offering four response options scored from 0 to 3. Participants are instructed to select the option that best describes how they have felt over the past two weeks. 
The total score is calculated by summing the scores for all 21 items, with higher scores indicating greater severity of depressive symptoms.

The STAI-5 [@zsido2020development] was used as a ground truth measure of anxiety. This abridged version of the STAI (**TODO: add ref**) includes 5 items rated on a 4-point Likert scale. Changes were made in the instructions from asking *"how participants feel right now"* to *"over the past 2 weeks"* to keep it consistent with the instructions of the PHQ-4 and BDI-II. A general score of anxiety was computed by averaging all the items.

Participants were also asked to complete two questionnaires of interoception, namely the Interoceptive Accuracy Scale [IAS - 21 items rated on analog scales, @murphy2020testing] and the Multidimensional Assessment of Interoceptive Awareness [MAIA-2 - 37 items, @mehling2018multidimensional].

After demographic questions, participants were asked to report the current presence of psychiatric issues (from a list), as well as the usage of treatment (antidepressants, mood stabilizers, anxiolytics, therapy). We indexed the presence of a depression when participants reported suffering from either Major Depressive Disorder (MDD) or Dysthymia, as well as undergoing a medical treatment. Similarly, we indexed the presence of an anxiety disorder when participants reported suffering from either Generalized Anxiety Disorder (GAD) or Panic Disorder, as well as undergoing a medical treatment.

@@

The original or refined version of the PHQ-4 was followed by the BDI-II, STAIT-5, IAS, and MAIA-2, presented in random order. The IAS and the MAIA-2 were included as part of another study focused on interoception, and were only used as part in this study of participation quality control.
